### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:18	14:02:26	(Tue18.Mar)
...

\ai{You are right that subarray averaging is important in our study. But we believe that "subarray MVDR" would be misleading, as to the best of our knowledge this term is usually used to describe the use of subarrays to reduce complexity, while we average over subarrays to deal with the coherent echoes present in \emph{active} systems. We still apply the weights to the full array. To avoid confusion we have now stated this better up front in the article (section I paragraph 5).}

@@

\ans{Thank you, it seems we should state this better upfront. In the 5th paragraph of the introduction we now explain that our system is a well sampled wideband sonar.}

@@

\ai{Thank you, we realize that this was not clear enough in the article. The 32 elements are evenly spaced along the 1.2m array, so:

@@

\ai{Thank you for pointing this out, we agree that this should be clarified. The array configuration produce the first grating lobes at $\theta = \text{arcsin}(\lambda M/D) = 23.5^\circ$, but this is not a problem since the element opening angle is $25^\circ$ ($\theta\in[12.5^\circ,12.5^\circ]$) at $f_c=100$\;kHz. In the paper we addition we perform sidescan imaging where only very narrow beams need to be beamformed. These details are now included in the paper, some in the 5th paragraph of the introduction and some in the first paragraph of section IV.}

@@

\ai{Thank you. We mention in the beginning of section IIA that we pre-steer to every angle and range bin in the image, but now repeat this in IIA paragraph 3, and state that we operate in wideband conditions in the introduction.}

@@

\ai{Again, thank you for a helpful remark, we will clarify this as well. After pulse compressing a chirp using the full transceiver bandwidth (30~kHz) range resolution is roughly $\Delta r \approx \frac{1}{B} = 2.5$~cm, which corresponds to a sample shift of just 1.2\footnote{$\Delta n = \frac{\Delta r f_s}{c} = 1.2$}. Hence we cover the entire pulse compressed signal with only a few samples. $K=2$ corresponds to a window length of $2K+1=5$ samples, as is shown by (4) in the article. Some edits have been made to make this clearer.} 

@@

\ai{Thank you, we understand how the confusion might arise. We operate under near field conditions and are indeed performing wavefront curvature beamforming. Hence, the index $n$ just an index over time at a resolution given by the sampling frequency. This has now been clarified.}

@@

\begin{enumerate}
\qi{It is unfortunate that so little effort was made to speed up the CPU versions of the code. For example, there are public-domain versions of optimized LAPACK libraries that provide the same sort of linear algebra codes as the authors used in their CPU implementation (for example, GoToBLAS, or Intel's MKL libraries).}
\ai{Thank you. We have now included our reasons for not comparing with an optimized CPU implementation.  One reason is that we have not been able to find any CPU batch solvers out there and lacked the time to make our own. In our tests our custom inline Cholesky solver beat alternatives from e.g. MKL as our matrices are too small to justify the extra function call overhead. Another reason is that to make the comparison fair we feel an equal effort would have to put into writing a covariance builder for the CPU, and to minimize data movement in each step and in between them. The details may be found in section V paragraph 2.}
%
\qi{The extra input/output of data to the GPU is a burden only on the GPU implementation, so would penalize the GPU implementation only, unless the authors were to "hide" the i/o by setting it up to run in parallel with the CPU processing, which is easier and easier with the latest GPU architectures. This should perhaps be pointed out.}
\ai{Yes this is a good point. Included in last paragraph of section IV.}
%
\qi{The authors do not provide much information about the GPU hardware they used, the NVIDIA Quadro 6000. How does this compare to the desktop video cards that reside in most desktop, workstation, server and even high-end laptop systems? What is the vintage of the architecture of this GPU? How has the architecture evolved? For example, the authors tell us the Quadro 6000 (\$1900, 6GB VRAM, 448 cores) is a Fermi architecture - this is the previous architecture, having been superceded by the Kepler architecture, with a new Quadro K6000 board (\$3600, 12 GB VRAM, 2880 cores). The Quadro boards are high-end boards with video output targeting the CADAM market - there are many cheaper alternatives targeted at gamers and an even more expensive compute-only board called TESLA targeted at high performance computing. It's difficult to say how much of this irrelevant.}
\ai{There is certainly a potential for comparing with many other cards here, but we decided to be thorough with one architecture than to compare with everything. To the paragraph introducing the Quadro 6000 we have explained what its equivalent consumer grade Geforce card would be. We have also included remarks that we expect Kepler to perform better had the design been optimized for it.}
%
\qi{The authors state that OpenCL is an equally attractive alternative to CUDA. This would be the case if the authors had been able to find something in OpenCL akin to the recently released batch-optimized linear solver code for CUDA. Unfortunately, this is a pervasive story - the support for scientific programming in CUDA is years ahead of OpenCL. The benefit of OpenCL is that it is supposed to be "cross-platform", which is true in theory, but it is hard to imagine being true in practice considering the wide range of heterogeneous computing elements OpenCL is supposed to cover; from phones to DSP chips to FPGAs. }
\ai{These are important remarks, thank you. We have written OpenCL programs too, and run them on Intel CPUs and GPUs from AMD and Nvidia. It was no walk in the park, but with a satisfactory end result. But like you say, these are just a subset of devices that OpenCL support, and we have now changed the wording to be more specific here. Your remark on the lack a batched linear solver is spot in, the sentence is now rewritten.}
\end{enumerate}

@@

\ans{You are absolutely right. The copy will be serialized due to divergent branching. It is unfortunate that no Cholesky based batch linear equation solver exist, which would have eliminated the need for the lower triangular... The paragraph has been edited to explain this better.}

@@

\begin{enumerate}
\qi{What does somebody need to program in CUDA? Authors can mention that CUDA C is just C with a few extra language features to specify how to distribute the work across the cores. Authors can mention that there is a nvcc compiler, a profiler, a debugger, math libraries (CUFFT, CUBLAS), and a large number of examples of varying complexity, all from NVIDIA. Authors can mention that CUDA can be used on Windows, MacOSX, or Linux, with an NVIDIA graphics card. Authors can mention that there are also third party CUDA interfaces in Fortran and Python. When discussing the batch-optimized linear solver code from NVIDIA, the authors should cite the NVIDIA site, and also links to CULA and MAGMA, other CUDA versions of LAPACK or subsets thereof.}
\ai{These are good suggestions. We have added some of these suggestions to the paragraph where we introduce CUDA, but regrettably had to leave some of it out due to space considerations. Citation to the "Nvidia Registered Developers Program" is added where we speak of the batch solver.}
%
\qi{Problems need to have high "arithmetic intensity" (the authors use "computational intensity") so that the cores stay busy. If there is not enough arithmetic, the cores sit idle waiting for data to be moved around. The authors do a nice job describing this situation on page 4 and the start of page 5.}
\ai{We thank the reviewer for those kind words. In the mentioned context we agree that "arithmetic" is likely a better alternative to "computational", and will make the relevant edits.}
%
\qi{The authors use the term "arithmetic reduction". Unfortunately, reduction is an important word/topic in GPU work. Perhaps "minimizing arithmetic operations" would be better. Reduction is any N-to-1 mapping, which poses a conundrum for N cores having to combine their individual results at a single location all at the same time... you don't want the cores to all line up and wait their turn.}
\ai{Yet again, very true! The reviewer's suggestion is much better, we have used it.}
%
\qi{On page 4, the authors talk about avoiding global memory, without getting into "coalesced" memory access patterns. This might merit a mention - for example, is at best only able to move one float for every 30 floats processed, and potentially much worse if care is not taken to use "coalesced memory access patterns (that avoid memory bank conflicts)". On page 5, the authors talk about "a collective access pattern that maximizes global memory bandwidth". Here too, the authors should perhaps use the "coalesced" term, since this is the term used in all of the GPGPU documentation.}
\ai{You are right. It is better to use the "official" terms. We have applied your suggestions.}
\end{enumerate}

@@

\ai{Thank you, both suggestions are now included.}

@@

@@

>>>>

\ai{The reviewer is right that subarray averaging is important in our study. But we believe that "subarray MVDR" would be misleading, as to the best of our knowledge this term is usually used to describe the use of subarrays to reduce complexity, while we average over subarrays to deal with the coherent echoes present in \emph{active} systems. We still apply the weights to the full array. To avoid confusion we have now stated this better up front in the article (section I paragraph 5).}

@@

\ans{We thank the reviewer for these remarks, it seems we should state this better upfront. In the 5th paragraph of the introduction we now explain that our system is a well sampled wideband sonar.}

@@

\ai{The reviewer made us realize that this was not clear enough in the article. The 32 elements are evenly spaced along the 1.2m array, so:

@@

\ai{Appreciations for pointing this out. We agree that this should be clarified. The array configuration produce the first grating lobes at $\theta = \text{arcsin}(\lambda M/D) = 23.5^\circ$, but this is not a problem since the element opening angle is $25^\circ$ ($\theta\in[12.5^\circ,12.5^\circ]$) at $f_c=100$\;kHz. In the paper we addition we perform sidescan imaging where only very narrow beams need to be beamformed. These details are now included in the paper, some in the 5th paragraph of the introduction and some in the first paragraph of section IV.}

@@

\ai{We mention in the beginning of section IIA that we pre-steer to every angle and range bin in the image, but now repeat this in IIA paragraph 3, and state that we operate in wideband conditions in the introduction.}

@@

\ai{Again, a helpful remark, we will clarify this as well. After pulse compressing a chirp using the full transceiver bandwidth (30~kHz) range resolution is roughly $\Delta r \approx \frac{1}{B} = 2.5$~cm, which corresponds to a sample shift of just 1.2\footnote{$\Delta n = \frac{\Delta r f_s}{c} = 1.2$}. Hence we cover the entire pulse compressed signal with only a few samples. $K=2$ corresponds to a window length of $2K+1=5$ samples, as is shown by (4) in the article. Some edits have been made to make this clearer.} 

@@

\ai{We understand how the confusion might arise. We operate under near field conditions and are indeed performing wavefront curvature beamforming. Hence, the index $n$ just an index over time at a resolution given by the sampling frequency. This has now been clarified.}

@@

\begin{enumerate}
\qi{It is unfortunate that so little effort was made to speed up the CPU versions of the code. For example, there are public-domain versions of optimized LAPACK libraries that provide the same sort of linear algebra codes as the authors used in their CPU implementation (for example, GoToBLAS, or Intel's MKL libraries).}
\ai{We agree, and have now included our reasons for not comparing with an optimized CPU implementation.  One reason is that we have not been able to find any CPU batch solvers out there and lacked the time to make our own. In our tests our custom inline Cholesky solver beat alternatives from e.g. MKL as our matrices are too small to justify the extra function call overhead. Another reason is that to make the comparison fair we feel an equal effort would have to put into writing a covariance builder for the CPU, and to minimize data movement in each step and in between them. The details may be found in section V paragraph 2.}
%
\qi{The extra input/output of data to the GPU is a burden only on the GPU implementation, so would penalize the GPU implementation only, unless the authors were to "hide" the i/o by setting it up to run in parallel with the CPU processing, which is easier and easier with the latest GPU architectures. This should perhaps be pointed out.}
\ai{Yes this is a good point. Included in last paragraph of section IV.}
%
\qi{The authors do not provide much information about the GPU hardware they used, the NVIDIA Quadro 6000. How does this compare to the desktop video cards that reside in most desktop, workstation, server and even high-end laptop systems? What is the vintage of the architecture of this GPU? How has the architecture evolved? For example, the authors tell us the Quadro 6000 (\$1900, 6GB VRAM, 448 cores) is a Fermi architecture - this is the previous architecture, having been superceded by the Kepler architecture, with a new Quadro K6000 board (\$3600, 12 GB VRAM, 2880 cores). The Quadro boards are high-end boards with video output targeting the CADAM market - there are many cheaper alternatives targeted at gamers and an even more expensive compute-only board called TESLA targeted at high performance computing. It's difficult to say how much of this irrelevant.}
\ai{There is certainly a potential for comparing with many other cards here, but we decided to be thorough with one architecture than to compare with everything. To the paragraph introducing the Quadro 6000 we have explained what its equivalent consumer grade Geforce card would be. We have also included remarks that we expect Kepler to perform better had the design been optimized for it.}
%
\qi{The authors state that OpenCL is an equally attractive alternative to CUDA. This would be the case if the authors had been able to find something in OpenCL akin to the recently released batch-optimized linear solver code for CUDA. Unfortunately, this is a pervasive story - the support for scientific programming in CUDA is years ahead of OpenCL. The benefit of OpenCL is that it is supposed to be "cross-platform", which is true in theory, but it is hard to imagine being true in practice considering the wide range of heterogeneous computing elements OpenCL is supposed to cover; from phones to DSP chips to FPGAs. }
\ai{These are important remarks, thank you. We have written OpenCL programs too, and run them on Intel CPUs and GPUs from AMD and Nvidia. It was no walk in the park, but with a satisfactory end result. But like you say, these are just a subset of devices that OpenCL support, and we have now changed the wording to be more specific here. Your remark on the lack a batched linear solver is spot in, the sentence is now rewritten.}
\end{enumerate}

@@

\ans{The reviewer is absolutely right. The copy will be serialized due to divergent branching. It is unfortunate that no Cholesky based batch linear equation solver exist, which would have eliminated the need for the lower triangular... The paragraph has been edited to explain this better.}

@@

\begin{enumerate}
\qi{What does somebody need to program in CUDA? Authors can mention that CUDA C is just C with a few extra language features to specify how to distribute the work across the cores. Authors can mention that there is a nvcc compiler, a profiler, a debugger, math libraries (CUFFT, CUBLAS), and a large number of examples of varying complexity, all from NVIDIA. Authors can mention that CUDA can be used on Windows, MacOSX, or Linux, with an NVIDIA graphics card. Authors can mention that there are also third party CUDA interfaces in Fortran and Python. When discussing the batch-optimized linear solver code from NVIDIA, the authors should cite the NVIDIA site, and also links to CULA and MAGMA, other CUDA versions of LAPACK or subsets thereof.}
\ai{These are good suggestions. We have added some of these suggestions to the paragraph where we introduce CUDA, but regrettably had to leave some of it out due to space considerations. Citation to the "Nvidia Registered Developers Program" is added where we speak of the batch solver.}
%
\qi{Problems need to have high "arithmetic intensity" (the authors use "computational intensity") so that the cores stay busy. If there is not enough arithmetic, the cores sit idle waiting for data to be moved around. The authors do a nice job describing this situation on page 4 and the start of page 5.}
\ai{We thank the reviewer for those kind words. In the mentioned context we agree that "arithmetic" is likely a better alternative to "computational", and will make the relevant edits.}
%
\qi{The authors use the term "arithmetic reduction". Unfortunately, reduction is an important word/topic in GPU work. Perhaps "minimizing arithmetic operations" would be better. Reduction is any N-to-1 mapping, which poses a conundrum for N cores having to combine their individual results at a single location all at the same time... you don't want the cores to all line up and wait their turn.}
\ai{Yet again, very true! The reviewer's suggestion is much better, we have used it.}
%
\qi{On page 4, the authors talk about avoiding global memory, without getting into "coalesced" memory access patterns. This might merit a mention - for example, is at best only able to move one float for every 30 floats processed, and potentially much worse if care is not taken to use "coalesced memory access patterns (that avoid memory bank conflicts)". On page 5, the authors talk about "a collective access pattern that maximizes global memory bandwidth". Here too, the authors should perhaps use the "coalesced" term, since this is the term used in all of the GPGPU documentation.}
\ai{The reviewer is right. It is better to use the "official" terms. We have applied the suggestions.}
\end{enumerate}

@@

\ai{Good point, both suggestions are now included.}

@@

\ai{TODO}

@@

\ai{Good suggestions. They are now added to the last paragraph of section V.}
